High-level cognition during story listening is reflected in high-order dynamic correlations in neural activity patterns

### 2021-08-02 paper/main.tex
added bibliography to end of text

\bibliographystyle{naturemag}
\bibliography{CDL-bibliography/cdl}

>>>>

\bibliographystyle{naturemag}
%\bibliography{CDL-bibliography/cdl}

\begin{thebibliography}{10}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\providecommand{\bibinfo}[2]{#2}
\providecommand{\eprint}[2][]{\url{#2}}

\bibitem{HaxbEtal01}
\bibinfo{author}{Haxby, J.~V.} \emph{et~al.}
\newblock \bibinfo{title}{Distributed and overlapping representations of faces
  and objects in ventral temporal cortex}.
\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{293}},
  \bibinfo{pages}{2425--2430} (\bibinfo{year}{2001}).

\bibitem{NormEtal06b}
\bibinfo{author}{Norman, K.~A.}, \bibinfo{author}{Polyn, S.~M.},
  \bibinfo{author}{Detre, G.~J.} \& \bibinfo{author}{Haxby, J.~V.}
\newblock \bibinfo{title}{Beyond mind-reading: multi-voxel pattern analysis of
  {fMRI} data}.
\newblock \emph{\bibinfo{journal}{Trends in Cognitive Sciences}}
  \textbf{\bibinfo{volume}{10}}, \bibinfo{pages}{424--430}
  (\bibinfo{year}{2006}).

\bibitem{TongPrat12}
\bibinfo{author}{Tong, F.} \& \bibinfo{author}{Pratte, M.~S.}
\newblock \bibinfo{title}{Decoding patterns of human brain activity}.
\newblock \emph{\bibinfo{journal}{Annual Review of Psychology}}
  \textbf{\bibinfo{volume}{63}}, \bibinfo{pages}{483--509}
  (\bibinfo{year}{2012}).

\bibitem{MitcEtal08a}
\bibinfo{author}{Mitchell, T.~M.} \emph{et~al.}
\newblock \bibinfo{title}{Predicting human brain activity associated with the
  meanings of nouns}.
\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{320}},
  \bibinfo{pages}{1191} (\bibinfo{year}{2008}).

\bibitem{KamiTong05}
\bibinfo{author}{Kamitani, Y.} \& \bibinfo{author}{Tong, F.}
\newblock \bibinfo{title}{Decoding the visual and subjective contents of the
  human brain}.
\newblock \emph{\bibinfo{journal}{Nature Neuroscience}}
  \textbf{\bibinfo{volume}{8}}, \bibinfo{pages}{679--685}
  (\bibinfo{year}{2005}).

\bibitem{NishEtal11}
\bibinfo{author}{Nishimoto, S.} \emph{et~al.}
\newblock \bibinfo{title}{Reconstructing visual experience from brain activity
  evoked by natural movies}.
\newblock \emph{\bibinfo{journal}{Current Biology}}
  \textbf{\bibinfo{volume}{21}}, \bibinfo{pages}{1--6} (\bibinfo{year}{2011}).

\bibitem{PereEtal18}
\bibinfo{author}{Pereira, F.} \emph{et~al.}
\newblock \bibinfo{title}{Toward a universal decoder of linguistic meaning from
  brain activation}.
\newblock \emph{\bibinfo{journal}{Nature Communications}}
  \textbf{\bibinfo{volume}{9}}, \bibinfo{pages}{1--13} (\bibinfo{year}{2018}).

\bibitem{HuthEtal12}
\bibinfo{author}{Huth, A.~G.}, \bibinfo{author}{Nisimoto, S.},
  \bibinfo{author}{Vu, A.~T.} \& \bibinfo{author}{Gallant, J.~L.}
\newblock \bibinfo{title}{A continuous semantic space describes the
  representation of thousands of object and action categories across the human
  brain}.
\newblock \emph{\bibinfo{journal}{Neuron}} \textbf{\bibinfo{volume}{76}},
  \bibinfo{pages}{1210--1224} (\bibinfo{year}{2012}).

\bibitem{HuthEtal16}
\bibinfo{author}{Huth, A.~G.}, \bibinfo{author}{de~Heer, W.~A.},
  \bibinfo{author}{Griffiths, T.~L.}, \bibinfo{author}{Theunissen, F.~E.} \&
  \bibinfo{author}{Gallant, J.~L.}
\newblock \bibinfo{title}{Natural speech reveals the semantic maps that tile
  human cerebral cortex}.
\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{532}},
  \bibinfo{pages}{453--458} (\bibinfo{year}{2016}).

\bibitem{EtzeEtal09}
\bibinfo{author}{Etzel, J.~A.}, \bibinfo{author}{Gazzola, V.} \&
  \bibinfo{author}{Keysers, C.}
\newblock \bibinfo{title}{An introduction to anatomical {ROI}-based {fMRI}
  classification}.
\newblock \emph{\bibinfo{journal}{Brain Research}}
  \textbf{\bibinfo{volume}{1281}}, \bibinfo{pages}{114--125}
  (\bibinfo{year}{2009}).

\bibitem{MannEtal18}
\bibinfo{author}{Manning, J.~R.} \emph{et~al.}
\newblock \bibinfo{title}{A probabilistic approach to discovering dynamic
  full-brain functional connectivity patterns}.
\newblock \emph{\bibinfo{journal}{{NeuroImage}}}
  \textbf{\bibinfo{volume}{180}}, \bibinfo{pages}{243--252}
  (\bibinfo{year}{2018}).

\bibitem{FongEtal19}
\bibinfo{author}{Fong, A. H.~C.} \emph{et~al.}
\newblock \bibinfo{title}{Dynamic functional connectivity during task
  performance and rest predicts individual differences in attention across
  studies}.
\newblock \emph{\bibinfo{journal}{{NeuroImage}}}
  \textbf{\bibinfo{volume}{188}}, \bibinfo{pages}{14--25}
  (\bibinfo{year}{2019}).

\bibitem{Gros88}
\bibinfo{author}{Grossberg, S.}
\newblock \bibinfo{title}{Nonlinear neural networks: principles, mechanisms,
  and architectures}.
\newblock \emph{\bibinfo{journal}{Neural Networks}}
  \textbf{\bibinfo{volume}{1}}, \bibinfo{pages}{17--61} (\bibinfo{year}{1988}).

\bibitem{Fris00}
\bibinfo{author}{Friston, K.~J.}
\newblock \bibinfo{title}{The labile brain. {I}. neuronal transients and
  nonlinear coupling}.
\newblock \emph{\bibinfo{journal}{Philosophical Transactions of the Royal
  Society of London}} \textbf{\bibinfo{volume}{355B}},
  \bibinfo{pages}{215--236} (\bibinfo{year}{2000}).

\bibitem{SporHone06}
\bibinfo{author}{Sporns, O.} \& \bibinfo{author}{Honey, C.~J.}
\newblock \bibinfo{title}{Small worlds inside big brains}.
\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
  Sciences, {USA}}} \textbf{\bibinfo{volume}{103}},
  \bibinfo{pages}{19219--19220} (\bibinfo{year}{2006}).

\bibitem{BassEtal06}
\bibinfo{author}{Bassett, D.}, \bibinfo{author}{Meyer-Lindenberg, A.},
  \bibinfo{author}{Achard, S.}, \bibinfo{author}{Duke, T.} \&
  \bibinfo{author}{Bullmore, E.}
\newblock \bibinfo{title}{Adaptive reconfiguration of fractal small-world human
  brain functional networks}.
\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
  Sciences, {USA}}} \textbf{\bibinfo{volume}{103}},
  \bibinfo{pages}{19518--19523} (\bibinfo{year}{2006}).

\bibitem{Turk13}
\bibinfo{author}{Turk-Browne, N.~B.}
\newblock \bibinfo{title}{Functional interactions as big data in the human
  brain}.
\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{342}},
  \bibinfo{pages}{580--584} (\bibinfo{year}{2013}).

\bibitem{DemeEtal19}
\bibinfo{author}{Demertzi, A.} \emph{et~al.}
\newblock \bibinfo{title}{Human consciousness is supported by dynamic complex
  patterns of brain signal coordination}.
\newblock \emph{\bibinfo{journal}{Science Advances}}
  \textbf{\bibinfo{volume}{5}}, \bibinfo{pages}{eaat7603}
  (\bibinfo{year}{2019}).

\bibitem{SoloEtal19}
\bibinfo{author}{Solomon, S.~H.}, \bibinfo{author}{Medaglia, J.~D.} \&
  \bibinfo{author}{Thompson-Schill, S.~L.}
\newblock \bibinfo{title}{Implementing a concept network model}.
\newblock \emph{\bibinfo{journal}{Behavior Research Methods}}
  \textbf{\bibinfo{volume}{51}}, \bibinfo{pages}{1717--1736}
  (\bibinfo{year}{2019}).

\bibitem{LuriEtal18}
\bibinfo{author}{Lurie, D.} \emph{et~al.}
\newblock \bibinfo{title}{On the nature of time-varying functional connectivity
  in resting f{MRI}}.
\newblock \emph{\bibinfo{journal}{{PsyArXiv}}}
  \textbf{\bibinfo{volume}{doi.org/10.31234/osf.io/xtzre}}
  (\bibinfo{year}{2018}).

\bibitem{PretEtal17}
\bibinfo{author}{Preti, M.~G.}, \bibinfo{author}{Bolton, T. A.~W.} \&
  \bibinfo{author}{{Van De Ville}, D.}
\newblock \bibinfo{title}{The dynamic functional connectome: state-of-the-art
  and perspectives}.
\newblock \emph{\bibinfo{journal}{{NeuroImage}}}
  \textbf{\bibinfo{volume}{160}}, \bibinfo{pages}{41--54}
  (\bibinfo{year}{2017}).

\bibitem{ZouEtal19}
\bibinfo{author}{Zou, Y.}, \bibinfo{author}{Donner, R.~V.},
  \bibinfo{author}{Marwan, N.}, \bibinfo{author}{Donges, J.~F.} \&
  \bibinfo{author}{Kurths, J.}
\newblock \bibinfo{title}{Complex network approaches to nonlinear time series
  analysis}.
\newblock \emph{\bibinfo{journal}{Physics Reports}}
  \textbf{\bibinfo{volume}{787}}, \bibinfo{pages}{1--97}
  (\bibinfo{year}{2019}).

\bibitem{MackEtal17}
\bibinfo{author}{Mack, M.~L.}, \bibinfo{author}{Preston, A.~R.} \&
  \bibinfo{author}{Love, B.~C.}
\newblock \bibinfo{title}{Medial prefrontal cortex compresses concept
  representations through learning}.
\newblock \emph{\bibinfo{journal}{{bioRxiv}}}
  \textbf{\bibinfo{volume}{doi.org/10.1101/178145}} (\bibinfo{year}{2017}).

\bibitem{BresKels01}
\bibinfo{author}{Bressler, S.~L.} \& \bibinfo{author}{Kelso, J. A.~S.}
\newblock \bibinfo{title}{Cortical coordination dynamics and cognition}.
\newblock \emph{\bibinfo{journal}{Trends in Cognitive Sciences}}
  \textbf{\bibinfo{volume}{5}}, \bibinfo{pages}{26--36} (\bibinfo{year}{2001}).

\bibitem{McIn00}
\bibinfo{author}{McIntosh, A.~R.}
\newblock \bibinfo{title}{Towards a network theory of cognition}.
\newblock \emph{\bibinfo{journal}{Neural Networks}}
  \textbf{\bibinfo{volume}{13}}, \bibinfo{pages}{861--870}
  (\bibinfo{year}{2000}).

\bibitem{ReimEtal17}
\bibinfo{author}{Reimann, M.~W.} \emph{et~al.}
\newblock \bibinfo{title}{Cliques of neurons bound into cavities provide a
  missing link between structure and function}.
\newblock \emph{\bibinfo{journal}{Frontiers in Computational Neuroscience}}
  \textbf{\bibinfo{volume}{11}}, \bibinfo{pages}{1--16} (\bibinfo{year}{2017}).

\bibitem{BeatEtal16}
\bibinfo{author}{Beaty, R.~E.}, \bibinfo{author}{Benedek, M.},
  \bibinfo{author}{Silvia, P.~J.} \& \bibinfo{author}{Schacter, D.~L.}
\newblock \bibinfo{title}{Creative cognition and brain network dynamics}.
\newblock \emph{\bibinfo{journal}{Trends in Cognitive Sciences}}
  \textbf{\bibinfo{volume}{20}}, \bibinfo{pages}{87--95}
  (\bibinfo{year}{2016}).

\bibitem{BullSpor09}
\bibinfo{author}{Bullmore, E.} \& \bibinfo{author}{Sporns, O.}
\newblock \bibinfo{title}{Complex brain networks: graph theoretical analysis of
  structural and functional systems}.
\newblock \emph{\bibinfo{journal}{Nature Reviews Neuroscience}}
  \textbf{\bibinfo{volume}{10}}, \bibinfo{pages}{186--198}
  (\bibinfo{year}{2009}).

\bibitem{Pear01}
\bibinfo{author}{Pearson, K.}
\newblock \bibinfo{title}{On lines and planes of closest fit to systems of
  points in space}.
\newblock \emph{\bibinfo{journal}{The London, Edinburgh, and Dublin
  Philosophical Magazine and Journal of Science}} \textbf{\bibinfo{volume}{2}},
  \bibinfo{pages}{559--572} (\bibinfo{year}{1901}).

\bibitem{McInJirs19}
\bibinfo{author}{Mc{I}ntosh, A.~R.} \& \bibinfo{author}{Jirsa, V.~K.}
\newblock \bibinfo{title}{The hidden repertoire of brain dynamics and
  dysfunction}.
\newblock \emph{\bibinfo{journal}{Network Neuroscience}}
  \textbf{\bibinfo{volume}{doi.org/10.1162/netn\_a\_00107}}
  (\bibinfo{year}{2019}).

\bibitem{TokeSomm19}
\bibinfo{author}{Toker, D.} \& \bibinfo{author}{Sommer, F.~T.}
\newblock \bibinfo{title}{Information integration in large brain networks}.
\newblock \emph{\bibinfo{journal}{{PLoS} Computational Biology}}
  \textbf{\bibinfo{volume}{15}}, \bibinfo{pages}{e1006807}
  (\bibinfo{year}{2019}).

\bibitem{GonzEtal19}
\bibinfo{author}{Gonzalez-Castillo, J.} \emph{et~al.}
\newblock \bibinfo{title}{Imaging the spontaneous flow of thought: distinct
  periods of cognition contribute to dynamic functional connectivity during
  test}.
\newblock \emph{\bibinfo{journal}{{NeuroImage}}} \textbf{\bibinfo{volume}{202}}
  (\bibinfo{year}{2019}).

\bibitem{Land95}
\bibinfo{author}{Landau, E.}
\newblock \bibinfo{title}{Zur relativen {Wertbemessung} der
  {Turnierresultate}}.
\newblock \emph{\bibinfo{journal}{Deutsches Wochenschach}}
  \textbf{\bibinfo{volume}{11}}, \bibinfo{pages}{366--369}
  (\bibinfo{year}{1895}).

\bibitem{BetzEtal19}
\bibinfo{author}{Betzel, R.~F.}, \bibinfo{author}{Byrge, L.},
  \bibinfo{author}{Esfahlani, F.~Z.} \& \bibinfo{author}{Kennedy, D.~P.}
\newblock \bibinfo{title}{Temporal fluctuations in the brain's modular
  architecture during movie-watching}.
\newblock \emph{\bibinfo{journal}{{bioRxiv}}}
  \textbf{\bibinfo{volume}{doi.org/10.1101/750919}} (\bibinfo{year}{2019}).

\bibitem{SizeEtal18}
\bibinfo{author}{Sizemore, A.~E.} \emph{et~al.}
\newblock \bibinfo{title}{Cliques and cavities in the human connectome}.
\newblock \emph{\bibinfo{journal}{Journal of Computational Neuroscience}}
  \textbf{\bibinfo{volume}{44}}, \bibinfo{pages}{115--145}
  (\bibinfo{year}{2018}).

\bibitem{SimoEtal16}
\bibinfo{author}{Simony, E.}, \bibinfo{author}{Honey, C.~J.},
  \bibinfo{author}{Chen, J.} \& \bibinfo{author}{Hasson, U.}
\newblock \bibinfo{title}{Dynamic reconfiguration of the default mode network
  during narrative comprehension}.
\newblock \emph{\bibinfo{journal}{Nature Communications}}
  \textbf{\bibinfo{volume}{7}}, \bibinfo{pages}{1--13} (\bibinfo{year}{2016}).

\bibitem{HassEtal08}
\bibinfo{author}{Hasson, U.}, \bibinfo{author}{Yang, E.},
  \bibinfo{author}{Vallines, I.}, \bibinfo{author}{Heeger, D.~J.} \&
  \bibinfo{author}{Rubin, N.}
\newblock \bibinfo{title}{A hierarchy of temporal receptive windows in human
  cortex}.
\newblock \emph{\bibinfo{journal}{The Journal of Neuroscience}}
  \textbf{\bibinfo{volume}{28}}, \bibinfo{pages}{2539--2550}
  (\bibinfo{year}{2008}).

\bibitem{RubiEtal17}
\bibinfo{author}{Rubin, T.~N.} \emph{et~al.}
\newblock \bibinfo{title}{Decoding brain activity using a large-scale
  probabilistic functional-anatomical atlas of human cognition}.
\newblock \emph{\bibinfo{journal}{{PLoS} Computational Biology}}
  \textbf{\bibinfo{volume}{13}}, \bibinfo{pages}{e1005649}
  (\bibinfo{year}{2017}).

\bibitem{ParkEtal18b}
\bibinfo{author}{Park, H.-J.}, \bibinfo{author}{Friston, K.~J.},
  \bibinfo{author}{Pae, C.}, \bibinfo{author}{Park, B.} \&
  \bibinfo{author}{Razi, A.}
\newblock \bibinfo{title}{Dynamic effective connectivity in resting state
  {fMRI}}.
\newblock \emph{\bibinfo{journal}{{NeuroImage}}}
  \textbf{\bibinfo{volume}{180}}, \bibinfo{pages}{594--608}
  (\bibinfo{year}{2018}).

\bibitem{RoyEtal19}
\bibinfo{author}{Roy, D.~S.} \emph{et~al.}
\newblock \bibinfo{title}{Brain-wide mapping of contextual fear memory engram
  ensembles supports the dispersed engram complex hypothesis}.
\newblock \emph{\bibinfo{journal}{{bioRxiv}}}
  \textbf{\bibinfo{volume}{doi.org/10.1101/668483}} (\bibinfo{year}{2019}).

\bibitem{LiegEtal19}
\bibinfo{author}{Li\'{e}geois, R.} \emph{et~al.}
\newblock \bibinfo{title}{Resting brain dynamics at different timescales
  capture distinct aspects of human behavior}.
\newblock \emph{\bibinfo{journal}{Nature Communications}}
  \textbf{\bibinfo{volume}{10}}, \bibinfo{pages}{1--9} (\bibinfo{year}{2019}).

\bibitem{ChanGlov10}
\bibinfo{author}{Chang, C.} \& \bibinfo{author}{Glover, G.~H.}
\newblock \bibinfo{title}{Time-frequency dynamics of resting-state brain
  connectivity measured with f{MRI}}.
\newblock \emph{\bibinfo{journal}{{NeuroImage}}} \textbf{\bibinfo{volume}{50}},
  \bibinfo{pages}{81--98} (\bibinfo{year}{2010}).

\bibitem{ZhenEtal19}
\bibinfo{author}{Zheng, M.}, \bibinfo{author}{Allard, A.},
  \bibinfo{author}{Hagmann, P.} \& \bibinfo{author}{Serrano, M. . .~A.}
\newblock \bibinfo{title}{Geometric renormalization unravels self-similarity of
  the multiscale human connectome}.
\newblock \emph{\bibinfo{journal}{{arXiv}}}
  \textbf{\bibinfo{volume}{1904.11793}} (\bibinfo{year}{2019}).

\bibitem{BaldEtal17}
\bibinfo{author}{Baldassano, C.} \emph{et~al.}
\newblock \bibinfo{title}{Discovering event structure in continuous narrative
  perception and memory}.
\newblock \emph{\bibinfo{journal}{Neuron}} \textbf{\bibinfo{volume}{95}},
  \bibinfo{pages}{709--721} (\bibinfo{year}{2017}).

\bibitem{HassEtal15}
\bibinfo{author}{Hasson, U.}, \bibinfo{author}{Chen, J.} \&
  \bibinfo{author}{Honey, C.~J.}
\newblock \bibinfo{title}{Hierarchical process memory: memory as an integral
  component of information processing}.
\newblock \emph{\bibinfo{journal}{Trends in Cognitive Sciences}}
  \textbf{\bibinfo{volume}{19}}, \bibinfo{pages}{304--315}
  (\bibinfo{year}{2015}).

\bibitem{HoneEtal12a}
\bibinfo{author}{Honey, C.~J.} \emph{et~al.}
\newblock \bibinfo{title}{Slow cortical dynamics and the accumulation of
  information over long timescales}.
\newblock \emph{\bibinfo{journal}{Neuron}} \textbf{\bibinfo{volume}{76}},
  \bibinfo{pages}{423--434} (\bibinfo{year}{2012}).

\bibitem{LernEtal11}
\bibinfo{author}{Lerner, Y.}, \bibinfo{author}{Honey, C.~J.},
  \bibinfo{author}{Silbert, L.~J.} \& \bibinfo{author}{Hasson, U.}
\newblock \bibinfo{title}{Topographic mapping of a hierarchy of temporal
  receptive windows using a narrated story}.
\newblock \emph{\bibinfo{journal}{The Journal of Neuroscience}}
  \textbf{\bibinfo{volume}{31}}, \bibinfo{pages}{2906--2915}
  (\bibinfo{year}{2011}).

\bibitem{LernEtal14}
\bibinfo{author}{Lerner, Y.}, \bibinfo{author}{Honey, C.~J.},
  \bibinfo{author}{Katkov, M.} \& \bibinfo{author}{Hasson, U.}
\newblock \bibinfo{title}{Temporal scaling of neural responses to compressed
  and dilated natural speech}.
\newblock \emph{\bibinfo{journal}{Journal of Neurophysiology}}
  \textbf{\bibinfo{volume}{111}}, \bibinfo{pages}{2433--2444}
  (\bibinfo{year}{2014}).

\bibitem{ChieHone19}
\bibinfo{author}{Chien, H.-Y.~S.} \& \bibinfo{author}{Honey, C.~J.}
\newblock \bibinfo{title}{Constructing and forgetting temporal context in the
  human cerebral cortex}.
\newblock \emph{\bibinfo{journal}{{bioRxiv}}}
  \textbf{\bibinfo{volume}{doi.org/10.1101/761593}} (\bibinfo{year}{2019}).

\bibitem{LeeEtal20}
\bibinfo{author}{Lee, C.~S.}, \bibinfo{author}{Aly, M.} \&
  \bibinfo{author}{Baldassano, C.}
\newblock \bibinfo{title}{Anticipation of temporally structured events in the
  brain}.
\newblock \emph{\bibinfo{journal}{{bioRxiv}}}
  \textbf{\bibinfo{volume}{10.1101/2020.10.14.338145}} (\bibinfo{year}{2020}).

\bibitem{FallEtal20}
\bibinfo{author}{Fallon, J.}, \bibinfo{author}{Ward, P. G.~D.},
  \bibinfo{author}{Parkes, L.} \& \bibinfo{author}{Oldham, S.}
\newblock \bibinfo{title}{Timescales of spontaneous {fMRI} fluctuations relate
  to structural connectivity in the brain}.
\newblock \emph{\bibinfo{journal}{Network Neuroscience}}
  \textbf{\bibinfo{volume}{4}}, \bibinfo{pages}{788--806}
  (\bibinfo{year}{2020}).

\bibitem{ShapEtal19}
\bibinfo{author}{Shappell, H.}, \bibinfo{author}{Caffo, B.~S.},
  \bibinfo{author}{Pekar, J.~J.} \& \bibinfo{author}{Lindquist, M.~A.}
\newblock \bibinfo{title}{Improved state change estimation in dynamic
  functional connectivity using hidden semi-{M}arkov models}.
\newblock \emph{\bibinfo{journal}{{NeuroImage}}}
  \textbf{\bibinfo{volume}{191}}, \bibinfo{pages}{243--257}
  (\bibinfo{year}{2019}).

\bibitem{VidaEtal18}
\bibinfo{author}{Vidaurre, D.} \emph{et~al.}
\newblock \bibinfo{title}{Discovering dynamic brain neworks from big data in
  rest and task}.
\newblock \emph{\bibinfo{journal}{{NeuroImage}}}
  \textbf{\bibinfo{volume}{180}}, \bibinfo{pages}{646--656}
  (\bibinfo{year}{2018}).

\bibitem{AlleEtal12b}
\bibinfo{author}{Allen, E.~A.} \emph{et~al.}
\newblock \bibinfo{title}{Tracking whole-brain connectivity dynamics in the
  resting state}.
\newblock \emph{\bibinfo{journal}{Cerebral Cortex}}
  \textbf{\bibinfo{volume}{24}}, \bibinfo{pages}{663--676}
  (\bibinfo{year}{2012}).

\bibitem{SimoChan20}
\bibinfo{author}{Simony, E.} \& \bibinfo{author}{Chang, C.}
\newblock \bibinfo{title}{Analysis of stimulus-induced brain dynamics during
  naturalistic paradigms}.
\newblock \emph{\bibinfo{journal}{{NeuroImage}}}
  \textbf{\bibinfo{volume}{216}}, \bibinfo{pages}{116461}
  (\bibinfo{year}{2020}).

\bibitem{Zar10}
\bibinfo{author}{Zar, J.~H.}
\newblock \emph{\bibinfo{title}{Biostatistical analysis}}
  (\bibinfo{publisher}{Prentice-Hall}, \bibinfo{year}{2010}).

\bibitem{TippBish99}
\bibinfo{author}{Tipping, M.~E.} \& \bibinfo{author}{Bishop, C.~M.}
\newblock \bibinfo{title}{Probabilistic principal component analysis}.
\newblock \emph{\bibinfo{journal}{Journal of Royal Statistical Society, Series
  {B}}} \textbf{\bibinfo{volume}{61}}, \bibinfo{pages}{611--622}
  (\bibinfo{year}{1999}).

\bibitem{Spea04}
\bibinfo{author}{Spearman, C.}
\newblock \bibinfo{title}{General intelligence, objectively determined and
  measured}.
\newblock \emph{\bibinfo{journal}{Americal Journal of Psychology}}
  \textbf{\bibinfo{volume}{15}}, \bibinfo{pages}{201--292}
  (\bibinfo{year}{1904}).

\bibitem{JuttHera91}
\bibinfo{author}{Jutten, C.} \& \bibinfo{author}{Herault, J.}
\newblock \bibinfo{title}{Blind separation of sources, part {I}: an adaptive
  algorithm based on neuromimetic architecture}.
\newblock \emph{\bibinfo{journal}{Signal Processing}}
  \textbf{\bibinfo{volume}{24}}, \bibinfo{pages}{1--10} (\bibinfo{year}{1991}).

\bibitem{ComoEtal91}
\bibinfo{author}{Comon, P.}, \bibinfo{author}{Jutten, C.} \&
  \bibinfo{author}{Herault, J.}
\newblock \bibinfo{title}{Blind separation of sources, part {II}: problems
  statement}.
\newblock \emph{\bibinfo{journal}{Signal Processing}}
  \textbf{\bibinfo{volume}{24}}, \bibinfo{pages}{11--20}
  (\bibinfo{year}{1991}).

\bibitem{vandHint08}
\bibinfo{author}{van~der Maaten, L. J.~P.} \& \bibinfo{author}{Hinton, G.~E.}
\newblock \bibinfo{title}{Visualizing high-dimensional data using {t-SNE}}.
\newblock \emph{\bibinfo{journal}{Journal of Machine Learning Research}}
  \textbf{\bibinfo{volume}{9}}, \bibinfo{pages}{2579--2605}
  (\bibinfo{year}{2008}).

\bibitem{McInEtal18}
\bibinfo{author}{McInnes, L.}, \bibinfo{author}{Healy, J.} \&
  \bibinfo{author}{Melville, J.}
\newblock \bibinfo{title}{{UMAP}: uniform manifold approximation and projection
  for dimension reduction}.
\newblock \emph{\bibinfo{journal}{{arXiv}}} \textbf{\bibinfo{volume}{1802}}
  (\bibinfo{year}{2018}).

\bibitem{LeeSeun99}
\bibinfo{author}{Lee, D.~D.} \& \bibinfo{author}{Seung, H.~S.}
\newblock \bibinfo{title}{Learning the parts of objects by non-negative matrix
  factorization}.
\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{401}},
  \bibinfo{pages}{788--791} (\bibinfo{year}{1999}).

\bibitem{MannEtal14b}
\bibinfo{author}{Manning, J.~R.}, \bibinfo{author}{Ranganath, R.},
  \bibinfo{author}{Norman, K.~A.} \& \bibinfo{author}{Blei, D.~M.}
\newblock \bibinfo{title}{Topographic factor analysis: a {B}ayesian model for
  inferring brain networks from neural data}.
\newblock \emph{\bibinfo{journal}{{PLoS} One}} \textbf{\bibinfo{volume}{9}},
  \bibinfo{pages}{e94914} (\bibinfo{year}{2014}).

\bibitem{GersEtal11}
\bibinfo{author}{Gershman, S.~J.}, \bibinfo{author}{Blei, D.~M.},
  \bibinfo{author}{Pereira, F.} \& \bibinfo{author}{Norman, K.~A.}
\newblock \bibinfo{title}{A topographic latent source model for {fMRI} data}.
\newblock \emph{\bibinfo{journal}{{NeuroImage}}} \textbf{\bibinfo{volume}{57}},
  \bibinfo{pages}{89--100} (\bibinfo{year}{2011}).

\bibitem{MairEtal09a}
\bibinfo{author}{Mairal, J.~B.}, \bibinfo{author}{Bach, F.},
  \bibinfo{author}{Ponce, J.} \& \bibinfo{author}{Sapiro, G.}
\newblock \bibinfo{title}{Online dictionary learning for sparse coding}.
\newblock \emph{\bibinfo{journal}{Proceedings of the International Conference
  on Machine Learning}} \bibinfo{pages}{689--696} (\bibinfo{year}{2009}).

\bibitem{MairEtal09b}
\bibinfo{author}{Mairal, J.}, \bibinfo{author}{Ponce, J.},
  \bibinfo{author}{Sapiro, G.}, \bibinfo{author}{Zisserman, A.} \&
  \bibinfo{author}{Bach, F.~R.}
\newblock \bibinfo{title}{Supervised dictionary learning}.
\newblock \emph{\bibinfo{journal}{Advances in Neural Information Processing
  Systems}} \bibinfo{pages}{1033--1040} (\bibinfo{year}{2009}).

\bibitem{HintSala06}
\bibinfo{author}{Hinton, G.~E.} \& \bibinfo{author}{Salakhutdinov, R.~R.}
\newblock \bibinfo{title}{Reducing the dimensionality of data with neural
  networks}.
\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{313}},
  \bibinfo{pages}{504--507} (\bibinfo{year}{2006}).

\bibitem{Newm05}
\bibinfo{author}{Newman, M. E.~J.}
\newblock \bibinfo{title}{A measure of betweenness centrality based on random
  walks}.
\newblock \emph{\bibinfo{journal}{Social Networks}}
  \textbf{\bibinfo{volume}{27}}, \bibinfo{pages}{39--54}
  (\bibinfo{year}{2005}).

\bibitem{OpsaEtal10}
\bibinfo{author}{Opsahl, T.}, \bibinfo{author}{Agneessens, F.} \&
  \bibinfo{author}{Skvoretz, J.}
\newblock \bibinfo{title}{Node centrality in weighted networks: generalizing
  degree and shortest paths}.
\newblock \emph{\bibinfo{journal}{Social Networks}}
  \textbf{\bibinfo{volume}{32}}, \bibinfo{pages}{245--251}
  (\bibinfo{year}{2010}).

\bibitem{Bart04}
\bibinfo{author}{Barth\'{e}lemy, M.}
\newblock \bibinfo{title}{Betweenness centrality in large complex networks}.
\newblock \emph{\bibinfo{journal}{{European} Physical Journal {B}}}
  \textbf{\bibinfo{volume}{38}}, \bibinfo{pages}{163--168}
  (\bibinfo{year}{2004}).

\bibitem{GeisEtal08}
\bibinfo{author}{Geisberger, R.}, \bibinfo{author}{Sanders, P.} \&
  \bibinfo{author}{Schultes, D.}
\newblock \bibinfo{title}{Better approximation of betweenness centrality}.
\newblock \emph{\bibinfo{journal}{Proceedings of the Meeting on Algorithm
  Engineering and Experiments}} \bibinfo{pages}{90--100}
  (\bibinfo{year}{2008}).

\bibitem{Free77}
\bibinfo{author}{Freeman, L.~C.}
\newblock \bibinfo{title}{A set of measures of centrality based on
  betweenness}.
\newblock \emph{\bibinfo{journal}{Sociometry}} \textbf{\bibinfo{volume}{40}},
  \bibinfo{pages}{35--41} (\bibinfo{year}{1977}).

\bibitem{Rao82}
\bibinfo{author}{Rao, C.~R.}
\newblock \bibinfo{title}{Diversity and dissimilarity coeficients: a unified
  approach}.
\newblock \emph{\bibinfo{journal}{Theoretical Population Biology}}
  \textbf{\bibinfo{volume}{21}}, \bibinfo{pages}{24--43}
  (\bibinfo{year}{1982}).

\bibitem{Lin09}
\bibinfo{author}{Lin, J.}
\newblock \bibinfo{title}{Divergence measures based on the {Shannon} entropy}.
\newblock \emph{\bibinfo{journal}{{IEEE} Transactions on Information Theory}}
  \textbf{\bibinfo{volume}{37}}, \bibinfo{pages}{145--151}
  (\bibinfo{year}{2009}).

\bibitem{RicoSzei06}
\bibinfo{author}{Ricotta, C.} \& \bibinfo{author}{Szeidl, L.}
\newblock \bibinfo{title}{Towards a unifying approach to diversity measures:
  bridging the gap between the {Shannon} entropy and {Rao's} quadratic index}.
\newblock \emph{\bibinfo{journal}{Theoretical Population Biology}}
  \textbf{\bibinfo{volume}{70}}, \bibinfo{pages}{237--243}
  (\bibinfo{year}{2006}).

\bibitem{Newm08}
\bibinfo{author}{Newman, M. E.~J.}
\newblock \bibinfo{title}{The mathematics of networks}.
\newblock \emph{\bibinfo{journal}{The New Palgrave Encyclopedia of Economics}}
  \textbf{\bibinfo{volume}{2}}, \bibinfo{pages}{1--12} (\bibinfo{year}{2008}).

\bibitem{Bona07}
\bibinfo{author}{Bonacich, P.}
\newblock \bibinfo{title}{Some unique properties of eigenvector centrality}.
\newblock \emph{\bibinfo{journal}{Social Networks}}
  \textbf{\bibinfo{volume}{29}}, \bibinfo{pages}{555--564}
  (\bibinfo{year}{2007}).

\bibitem{LohmEtal10}
\bibinfo{author}{Lohmann, G.} \emph{et~al.}
\newblock \bibinfo{title}{Eigenvector centrality mapping for analyzing
  connectivity patterns in {fMRI} data of the human brain}.
\newblock \emph{\bibinfo{journal}{{PLoS} One}} \textbf{\bibinfo{volume}{5}},
  \bibinfo{pages}{e10232} (\bibinfo{year}{2010}).
